### 2016-02-12 mcmc.tex
Fix a typo (?).

As we discuss briefly below (\sectionname~\ref{sec:methods}),
  there are many \MCMC\ methods more advanced than M--H.
However, they all share characteristics with M--H
  (initialization, tuning, judging convergence),
  such that it is very valuable to understand \MH\ well before using anything more advanced.
Furthermore, a scientist new to \MCMC\ benefits enormously from
  building, tuning, and using her or his own \MCMC\ software.
One piece of advice we give then,
  to the new user of \MCMC,
  is to code up, tune, and use a \MH\ \MCMC\ sampler for a scientific project.
A huge amount is learned in doing this,
  and it is very often the case that the home-built \MH\ \MCMC\ does everything needed;
  you often don't need any more advanced tool.
Only after you have concluded that your home-built \MH\ \MCMC\ sampler
  is not suited to your project
  (or not developed properly into a properly versatile software package)
  should you download and start to use any professionally developed alternative.
That is, even if---in the end---%
  you want to leave the sampling code to the experts and run an industrial-strength code,
  it is still valuable to build your own,
  given the simplicity of the algorithm,
  and given the intuition you gain by doing it (at least once) yourself.\note{%
    We also make this point in a previous \documentname\ (\citealt{fittingaline};
    the ambitious reader will find in that \documentname\ a solid example project
    for using \MCMC\ in a real context.}

>>>>

As we discuss briefly below (\sectionname~\ref{sec:methods}),
  there are many \MCMC\ methods more advanced than M--H.
However, they all share characteristics with M--H
  (initialization, tuning, judging convergence),
  such that it is very valuable to understand \MH\ well before using anything more advanced.
Furthermore, a scientist new to \MCMC\ benefits enormously from
  building, tuning, and using her or his own \MCMC\ software.
One piece of advice we give then,
  to the new user of \MCMC,
  is to code up, tune, and use a \MH\ \MCMC\ sampler for a scientific project.
A huge amount is learned in doing this,
  and it is very often the case that the home-built \MH\ \MCMC\ does everything needed;
  you often don't need any more advanced tool.
Only after you have concluded that your home-built \MH\ \MCMC\ sampler
  is not suited to your project
  (or not developed properly into a properly versatile software package)
  should you download and start to use any professionally developed alternative.
That is, even if---in the end---%
  you want to leave the sampling code to the experts and run an industrial-strength code,
  it is still valuable to build your own,
  given the simplicity of the algorithm,
  and given the intuition you gain by doing it (at least once) yourself.\note{%
    We also make this point in a previous \documentname\ (\citealt{fittingaline});
    the ambitious reader will find in that \documentname\ a solid example project
    for using \MCMC\ in a real context.}
